---
title: "R Final Project"
author: "Galen haggerty"
date: "12/15/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
This is my R Notebook for my final project regression

I am importing the necessary packages below:

```{r}
library(tidyverse)
```
I am uploading my final data
```{r}
finaldata = read.csv('/Users/galenhaggerty/Documents/GitHub/final-project-galenhaggerty/finaldata.csv')
```
Running my OLS regression

Gross Potential is my independent variable and my dependent variables are the Average Price (Gross/Attendance), average capacity, whether the show was an original or revival, and how many Tony's the production won.
```{r}
final <- lm(X..Gross.Pot. ~  Av..Price + X..Capacity + factor(Original.Revival) + Tonys , data = finaldata)
summary(final)
```
Results show 3 significant variables (Average Price, Capacity, and Tonys)

R^2 = .767, therefore we can explain away about 76.7% of the results

The average price of a ticket increasing by 1 dollar will increase gross potential by .12 percentage points (so if the average price of a ticket goes up by 10 dollars, you will see about a 1.2 percentage points increase towards gross potential revenue)

Unsurprisingly, a 1% increase in seats filled (capacity) will result in about a 1.2 percentage points increase in the gross potential

Winning 1 extra Tony award will increase the gross potential of a show by about 1.87 percentage points

Below is the output using stargazer:
```{r}
library(stargazer)
stargazer(final, type="text",
          title            = "Broadway Data Results",
          covariate.labels = c("Average Price", "Capacity", "Original/Revival", "Tonys", "Constant"),
          dep.var.labels   = "Gross Potential")
```